---
title: "Draft-Cleaning2/EDA"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Business Problem
The situation of Airbnb houses demand in Boston and Beijing. Compared it with the demand of hotels on Booking.com to futher discover the influence of competitor to Airbnb.

## Data Sources
Boston and Beijing Airbnb data: http://insideairbnb.com/get-the-data.html
Boston and Beijing Booking data: web crawler

Inside Airbnb is an non-commercial and independent dataset of Airbnb global demand, which includes the first-hand data of Airbnb booking history and reviews of users.

## Preprocessing Steps 
### Set up environment

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(readr)
library(lubridate)
library(ggthemes)
library(leaflet)
options(digits=9)
Sys.setlocale('LC_ALL','C')


```


### EDA Part 1 

# Data Reloading
```{r message=FALSE, warning=FALSE}
bj_reviews_cleaned <- read.csv('bj_reviews_cleaned.csv')
bos_reviews_cleaned <- read.csv('bos_reviews_cleaned.csv')
head(bj_reviews_cleaned)
```

```{r message=FALSE, warning=FALSE}
bj_list_cleaned <- read.csv('bj_list_cleaned.csv')
bos_list_cleaned <- read.csv('bos_list_cleaned.csv')
```

```{r message=FALSE, warning=FALSE}
bj_calendar_cleaned <- read.csv('bj_calendar_cleaned.csv')
head(bj_calendar_cleaned)
bos_calendar_cleaned <- read.csv('bos_calendar_cleaned.csv')

```

#limited Beijing city into 5-ring Road, which is the main part of Beijing excludes suburbs

```{r}
head(bos_list_cleaned)
summary(bj_list_cleaned$latitude);summary(bj_list_cleaned$longitude)

bj_list_cleaned2 <- subset(bj_list_cleaned, latitude <=39.9777778168 & latitude >= 39.8401771328)
bj_list_cleaned3 <- subset(bj_list_cleaned2,longitude>=116.2875366211 & longitude <=116.4787673950)
glimpse(bj_list_cleaned3)

write_csv(bj_list_cleaned3, 'bj_list_cleaned3.csv')
```

```{r}
str(bos_list_cleaned)
str(bj_calendar_cleaned)

str(bj_list_cleaned3)
```

# Graph 1
```{r}
bj_reviews_yr <- bj_reviews_cleaned %>%
  group_by(year) %>%  
  count(listing_id) %>% 
  arrange(desc(n)) 
bos_reviews_yr <- bos_reviews_cleaned%>% 
  group_by(year) %>% 
  count(listing_id) %>% 
  arrange(desc(n)) 


# bjl %>% select(id, name, number_of_reviews) %>% arrange(desc(number_of_reviews))
# bjl %>% select(id, name, number_of_reviews) %>% arrange(number_of_reviews)
# 23437 listings have reviews for Beijing
# 23437/38814
#bosl %>% select(id, name, number_of_reviews) %>% #arrange(desc(number_of_reviews))
# 3507 listings have reviews for Boston
# 3507/3585
# the rate of review in boston is higher than beijing 


ggplot(bj_reviews_yr,aes(x=as.factor(year),y=n))+
  geom_jitter(alpha=0.3,aes(color=n)) +
  geom_smooth() +
  theme_bw()+
  scale_fill_brewer() +ylim(0,200) +labs(title = 'How popular is Airbnb in Beijing', subtitle = 'Number of reviews received for a single listing over years',color='# of reviews') + xlab('Year') + ylab('The number of reviews')

ggplot(bos_reviews_yr,aes(x=as.factor(year),y=n))+
  geom_jitter(alpha=0.3,aes(color=n)) +
  geom_smooth() +
  theme_bw()+
  scale_fill_brewer() +ylim(0,200) +
  labs(title = 'How popular is Airbnb in Boston', subtitle = 'Number of reviews received for a single listing over years',color='# of reviews') +xlab('Year') + ylab('The number of reviews')
```

# Graph 2

```{r}
bos_list_cleaned_rmna <- bos_list_cleaned %>% 
  filter(!is.na(review_scores_rating)) %>% 
  filter(!is.na(host_is_superhost))

bj_list_cleaned_rmna <- bj_list_cleaned %>% 
  filter(!is.na(review_scores_rating)) %>% 
  filter(!is.na(host_is_superhost))

bos_list_cleaned_rmna$host_response_rate <- as.numeric(bos_list_cleaned_rmna$host_response_rate)
bj_list_cleaned_rmna$host_response_rate <- as.numeric(bj_list_cleaned_rmna$host_response_rate)

summary(bj_list_cleaned_rmna$host_response_rate)
summary(bos_list_cleaned_rmna$host_response_rate)

ggplot(bos_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=review_scores_rating)) + geom_boxplot() +
  theme_bw() +labs(title = 'Review Rating Scores by SuperHost in Boston') + xlab('Super Host or Not') + ylab('Review Rating in 100 pts Scale')


ggplot(bj_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=review_scores_rating)) + geom_boxplot() +
  theme_bw() +labs(title = 'Review Rating Scores by SuperHost in Beijing') + xlab('Super Host or Not') + ylab('Review Rating in 100 pts Scale')

# ggplot(bj_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=host_response_rate)) + geom_boxplot() +
#   theme_bw()
# 
# ggplot(bos_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=host_response_rate)) + geom_boxplot() +
#   theme_bw()


ggplot(bos_list_cleaned_rmna,aes(x=host_response_rate,y=review_scores_rating)) +
  geom_jitter(aes(color=as.factor(host_is_superhost)),alpha=0.3) +theme_bw() +labs(title = 'Indicators for SuperHost in Boston', subtitle = 'Avg. Rating by Response Rate', color = 'Is SuperHost') + xlab('Host Response Rate') + ylab('Review Rating in 100 pts Scale')

ggplot(bj_list_cleaned_rmna,aes(x=host_response_rate,y=review_scores_rating)) +
  geom_jitter(aes(color=as.factor(host_is_superhost)),alpha=0.3) +theme_bw() +
  labs(title = 'Indicators for SuperHost in Beijing', subtitle = 'Avg. Rating by Response Rate', color = 'Is SuperHost') + xlab('Host Response Rate') + ylab('Review Rating in 100 pts Scale')
```


# Graph 3
```{r}
bj_avgprice <- bj_calendar_cleaned%>% group_by(date) %>% summarise(avg_price = mean(price, na.rm = TRUE))
bj_avgprice

bj_avgprice<- bj_avgprice %>% mutate(day = strftime(date,'%A'), 
                                     indollarprice = avg_price/7)
bj_avgprice$day <- factor(bj_avgprice$day, levels=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), labels=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))


ggplot(bj_avgprice,aes(x=factor(day),y=indollarprice)) + 
  geom_boxplot(outlier.shape=NA,fill = "#FF5A5F",color = "#565A5C") + geom_jitter(alpha=0.05,width=0.1) +
  theme_bw() + 
  labs(title = 'Price Trends over the weekday & weekends in Beijing', subtitle = 'avgprice = Avg. price by day in U.S dollars') +xlab('weekday & weekends') +ylab('Average Price') +coord_cartesian(ylim = ylimbj)


bos_avgprice <- bos_calendar_cleaned%>% group_by(date) %>% summarise(avg_price = mean(price, na.rm = TRUE))
bos_avgprice

bos_avgprice<- bos_avgprice %>% mutate(day = strftime(date,'%A'))
bos_avgprice$day <- factor(bos_avgprice$day, levels=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"), labels=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))


ggplot(bos_avgprice,aes(x=factor(day),y=avg_price)) + 
   geom_boxplot(outlier.shape=NA,fill = "#FF5A5F",color = "#565A5C") + geom_jitter(alpha=0.05,width=0.1) +
  theme_bw() +
  labs(title = 'Price Trends over the weekday & weekends in Boston', subtitle = 'avgprice = Avg. price by day in U.S dolalrs') +xlab('weekday & weekends') +ylab('Average Price')
```




# Graph 4 

```{r}
# avg_price_bj_2019 <- bj_calendar_cleaned  %>% 
#     filter(year == 2019) %>% 
#   group_by(listing_id, month) %>% 
#   summarize(avgprice= mean(price,na.rm=T))
# 
# avg_price_bos_2019 <- bos_calendar_cleaned %>% 
#   filter(year == 2019) %>% 
#   group_by(listing_id, month) %>% 
#   summarize(avgprice=mean(price,na.rm=T))
# 
# ylim_bos<-boxplot.stats(avg_price_bos_2019$avgprice)$stats[c(1, 5)]
# ggplot(avg_price_bos_2019, aes(x = factor(month), y=avgprice)) + 
#   geom_boxplot(outlier.shape = NA) + 
#   coord_cartesian(ylim = ylim_bos * 1.5) +
#   theme_bw() + 
#   labs(title = 'Price Trends over the month in Boston', subtitle = 'avgprice = Avg. price by listing') +xlab('Months') +ylab('average price')
# 
# ylim_bj<-boxplot.stats(avg_price_bj_2019$avgprice)$stats[c(1, 5)]
# ggplot(avg_price_bj_2019, aes(x = factor(month), y=avgprice)) + 
#   geom_boxplot(outlier.shape = NA) + 
#   coord_cartesian(ylim = ylim_bos * 2.4) +
#   theme_bw() + 
#   labs(title = 'Price Trends over the month in Beijing', subtitle = 'avgprice = Avg. price by listing') + xlab('Months') +ylab('average price')
# 



bj_avgprice2<- bj_avgprice %>% mutate(month= strftime(date,'%m'), 
                                     indollarprice = avg_price/7)


ggplot(bj_avgprice2,aes(x=month,y=indollarprice)) + 
  geom_boxplot(outlier.shape=NA,fill = "#FF5A5F",color = "#565A5C") + geom_jitter(alpha=0.05,width=0.1) +
  theme_bw() + 
  labs(title = 'Price Trends over 12 months in Beijing', subtitle = 'avgprice = Avg. price by day in U.S dollars') +xlab('Months') +ylab('Average Price') 


bos_avgprice2<- bos_avgprice %>% mutate(month= strftime(date,'%m'), 
                                     indollarprice = avg_price/7)


ggplot(bos_avgprice2,aes(x=month,y=indollarprice)) + 
  geom_boxplot(outlier.shape=NA,fill = "#FF5A5F",color = "#565A5C") + geom_jitter(alpha=0.05,width=0.1) +
  theme_bw() + 
  labs(title = 'Price Trends over 12 months in Boston', subtitle = 'avgprice = Avg. price by day in U.S dollars') +xlab('Months') +ylab('Average Price') 




```


# Graph 5
```{r}
bosAirbnb <- bos_list_cleaned %>% 
  mutate(Log1pPrice = log1p(price), transformed_review = bos_list_cleaned$review_scores_rating^5)

bosAirbnb <- bosAirbnb %>% select(-price, -review_scores_rating)

pal <- colorNumeric(palette = rainbow(6), domain = bosAirbnb$Log1pPrice)

leaflet(data = bosAirbnb[is.na(bosAirbnb$Log1pPrice)==FALSE,]) %>%  
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   color = ~pal(Log1pPrice), weight = 1, radius=1.5, 
                   fillOpacity = 1, opacity = 1,
                   label = paste("Neighbourhood:", bosAirbnb$neighbourhood_cleansed)) %>% 
  addLegend("bottomright", pal = pal, values = ~Log1pPrice,
            title = "Log1pPrice",
            opacity = 1)


BJAirbnb <- bj_list_cleaned %>% 
  mutate(Log1pPrice = log1p(price), transformed_review = bj_list_cleaned$review_scores_rating^5)
BJAirbnb <- BJAirbnb %>% select(-price, -review_scores_rating)

pal <- colorNumeric(palette = rainbow(6), domain = BJAirbnb$Log1pPrice)

leaflet(data = BJAirbnb[is.na(BJAirbnb$Log1pPrice)==FALSE,]) %>%  
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   color = ~pal(Log1pPrice), weight = 1, radius=1.5, 
                   fillOpacity = 1, opacity = 1,
                   label = paste("Neighbourhood:", BJAirbnb$neighbourhood_cleansed)) %>% 
  addLegend("bottomright", pal = pal, values = ~Log1pPrice,
            title = "Log1pPrice",
            opacity = 1)



```

