---
title: "Draft-Cleaning/EDA"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Business Problem
The situation of Airbnb houses demand in Boston and Beijing. Compared it with the demand of hotels on Booking.com to futher discover the influence of competitor to Airbnb.

## Data Sources
Boston and Beijing Airbnb data: http://insideairbnb.com/get-the-data.html
Boston and Beijing Booking data: web crawler

Inside Airbnb is an non-commercial and independent dataset of Airbnb global demand, which includes the first-hand data of Airbnb booking history and reviews of users.

## Preprocessing Steps 
### Set up environment

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(readr)
library(lubridate)
library(ggthemes)
library(leaflet)
```


### EDA Part 1 

# Data Reloading
```{r message=FALSE, warning=FALSE}
bj_reviews_cleaned <- read.csv('bj_reviews_cleaned.csv')
bos_reviews_cleaned <- read.csv('bos_reviews_cleaned.csv')

```

```{r message=FALSE, warning=FALSE}
bj_list_cleaned <- read.csv('bj_list_cleaned.csv')
bos_list_cleaned <- read.csv('bos_list_cleaned.csv')
```

```{r message=FALSE, warning=FALSE}
bj_calendar_cleaned <- read.csv('bj_calendar_cleaned.csv')
bos_calendar_cleaned <- read.csv('bos_calendar_cleaned.csv')
```


# Graph 1
```{r}


bj_reviews_yr <- bj_reviews_cleaned %>%
  group_by(year) %>%  
  count(listing_id) %>% 
  arrange(desc(n)) 
bos_reviews_yr <- bos_reviews_cleaned%>% 
  group_by(year) %>% 
  count(listing_id) %>% 
  arrange(desc(n)) 


# bjl %>% select(id, name, number_of_reviews) %>% arrange(desc(number_of_reviews))
# bjl %>% select(id, name, number_of_reviews) %>% arrange(number_of_reviews)
# 23437 listings have reviews for Beijing
# 23437/38814
#bosl %>% select(id, name, number_of_reviews) %>% #arrange(desc(number_of_reviews))
# 3507 listings have reviews for Boston
# 3507/3585
# the rate of review in boston is higher than beijing 

ggplot(bj_reviews_yr,aes(x=as.factor(year),y=n))+
  geom_jitter(alpha=0.3,aes(color=n)) +
  geom_smooth() +
  theme_bw()+
  scale_fill_brewer() +ylim(0,250) +labs(title = 'How popular is Airbnb in Beijing', subtitle = 'Number of reviews received for a single listing over years',color='# of reviews') + xlab('Year') + ylab('The number of reviews')

ggplot(bos_reviews_yr,aes(x=as.factor(year),y=n))+
  geom_jitter(alpha=0.3,aes(color=n)) +
  geom_smooth() +
  theme_bw()+
  scale_fill_brewer() +ylim(0,250) +
  labs(title = 'How popular is Airbnb in Boston', subtitle = 'Number of reviews received for a single listing over years',color='# of reviews') +xlab('Year') + ylab('The number of reviews')


```

# Graph 2

```{r}

bos_list_cleaned_rmna <- bos_list_cleaned %>% 
  filter(!is.na(review_scores_rating)) %>% 
  filter(!is.na(host_is_superhost))

bj_list_cleaned_rmna <- bj_list_cleaned %>% 
  filter(!is.na(review_scores_rating)) %>% 
  filter(!is.na(host_is_superhost))

bos_list_cleaned_rmna$host_response_rate <- as.numeric(bos_list_cleaned_rmna$host_response_rate)
bj_list_cleaned_rmna$host_response_rate <- as.numeric(bj_list_cleaned_rmna$host_response_rate)

summary(bj_list_cleaned_rmna$host_response_rate)
summary(bos_list_cleaned_rmna$host_response_rate)

ggplot(bos_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=review_scores_rating)) + geom_boxplot() +
  theme_bw() +labs(title = 'Review Rating Scores by SuperHost in Boston') + xlab('Super Host or Not') + ylab('Review Rating in 100 pts Scale')


ggplot(bj_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=review_scores_rating)) + geom_boxplot() +
  theme_bw() +labs(title = 'Review Rating Scores by SuperHost in Beijing') + xlab('Super Host or Not') + ylab('Review Rating in 100 pts Scale')

# ggplot(bj_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=host_response_rate)) + geom_boxplot() +
#   theme_bw()
# 
# ggplot(bos_list_cleaned_rmna, aes(x=as.factor(host_is_superhost),                                                 y=host_response_rate)) + geom_boxplot() +
#   theme_bw()


ggplot(bos_list_cleaned_rmna,aes(x=host_response_rate,y=review_scores_rating)) +
  geom_jitter(aes(color=as.factor(host_is_superhost)),alpha=0.3) +theme_bw() +labs(title = 'Indicators for SuperHost in Boston', subtitle = 'Avg. Rating by Response Rate', color = 'Is SuperHost') + xlab('Host Response Rate') + ylab('Review Rating in 100 pts Scale')

ggplot(bj_list_cleaned_rmna,aes(x=host_response_rate,y=review_scores_rating)) +
  geom_jitter(aes(color=as.factor(host_is_superhost)),alpha=0.3) +theme_bw() +
  labs(title = 'Indicators for SuperHost in Beijing', subtitle = 'Avg. Rating by Response Rate', color = 'Is SuperHost') + xlab('Host Response Rate') + ylab('Review Rating in 100 pts Scale')
```


# Graph 3
```{r}
summary(bos_calendar_cleaned$year)

avg_price_bj <- bj_calendar_cleaned %>% 
  group_by(date, wkd) %>% 
  summarize(avgprice= mean(price, na.rm=T))

avg_price_bos <- bos_calendar_cleaned %>% 
  group_by(date, wkd) %>% 
  summarize(avgprice=mean(price,na.rm=T))

ggplot(avg_price_bos, aes(x=wkd, y=avgprice)) + 
  geom_boxplot() + geom_jitter(alpha=0.2) + 
  theme_bw() + 
  labs(title = 'Price Trends over the weekday & weekends in Boston', subtitle = 'avgprice = Avg. price by day') +xlab('weekday & weekends')

ggplot(avg_price_bj,aes(x=wkd,y=avgprice)) + 
  geom_boxplot(outlier.shape=NA) + geom_jitter(alpha=0.2) +
  theme_bw() + coord_cartesian(ylim = c(375, 420))+
  labs(title = 'Price Trends over the weekday & weekends in Beijing', subtitle = 'avgprice = Avg. price by day') +xlab('weekday & weekends')
```

# Graph 4 

```{r}
avg_price_bj_2020 <- bj_calendar_cleaned %>% 
  filter(year == 2020) %>% 
  group_by(listing_id, month) %>% 
  summarize(avgprice= mean(price,na.rm=T))

avg_price_bos_2020 <- bos_calendar_cleaned %>% 
  filter(year == 2020) %>% 
  group_by(listing_id, month) %>% 
  summarize(avgprice=mean(price,na.rm=T))

ylim_bos<-boxplot.stats(avg_price_bos_2020$avgprice)$stats[c(1, 5)]
ggplot(avg_price_bos_2020, aes(x = factor(month), y=avgprice)) + 
  geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim_bos * 1.5) +
  theme_bw() + 
  labs(title = 'Price Trends over the month in Boston', subtitle = 'avgprice = Avg. price by listing') +xlab('Months') +ylab('average price')

ylim_bj<-boxplot.stats(avg_price_bj_2020$avgprice)$stats[c(1, 5)]
ggplot(avg_price_bj_2020, aes(x = factor(month), y=avgprice)) + 
  geom_boxplot(outlier.shape = NA) + 
  coord_cartesian(ylim = ylim_bos * 2.4) +
  theme_bw() + 
  labs(title = 'Price Trends over the month in Beijing', subtitle = 'avgprice = Avg. price by listing') + xlab('Months') +ylab('average price')
```


# Graph 5
```{r}
bosAirbnb <- bos_list_cleaned %>% 
  mutate(Log1pPrice = log1p(price), transformed_review = bos_list_cleaned$review_scores_rating^5)

bosAirbnb <- bosAirbnb %>% select(-price, -review_scores_rating)

pal <- colorNumeric(palette = rainbow(6), domain = bosAirbnb$Log1pPrice)

leaflet(data = bosAirbnb[is.na(bosAirbnb$Log1pPrice)==FALSE,]) %>%  
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   color = ~pal(Log1pPrice), weight = 1, radius=1.5, 
                   fillOpacity = 1, opacity = 1,
                   label = paste("Neighbourhood:", bosAirbnb$neighbourhood_cleansed)) %>% 
  addLegend("bottomright", pal = pal, values = ~Log1pPrice,
            title = "Log1pPrice",
            opacity = 1)


BJAirbnb <- bj_list_cleaned %>% 
  mutate(Log1pPrice = log1p(price), transformed_review = bj_list_cleaned$review_scores_rating^5)
BJAirbnb <- BJAirbnb %>% select(-price, -review_scores_rating)

pal <- colorNumeric(palette = rainbow(6), domain = BJAirbnb$Log1pPrice)

leaflet(data = BJAirbnb[is.na(BJAirbnb$Log1pPrice)==FALSE,]) %>%  
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   color = ~pal(Log1pPrice), weight = 1, radius=1.5, 
                   fillOpacity = 1, opacity = 1,
                   label = paste("Neighbourhood:", BJAirbnb$neighbourhood_cleansed)) %>% 
  addLegend("bottomright", pal = pal, values = ~Log1pPrice,
            title = "Log1pPrice",
            opacity = 1)



```

